Two genera pathway association

### 2020-01-17 scripts/32_two_genera.Rmd
update

>>>>

genus_no_bact <- genus %>% 
  separate(pw, into = c('pathway','genus'), '\\|') %>% 
  mutate(genus = str_replace(genus, 'g__','')) %>% 
  filter(!genus %in% bac_genera) %>% 
  filter(genus != 'unclassified')

genus_no_bact_matrix <- genus_no_bact %>% 
  select(-genus) %>% 
  gather(key = 'sampleid', value = 'CPM', names(.)[2]:names(.)[ncol(.)]) %>% 
  group_by(pathway, sampleid) %>% 
  summarise(cpm = sum(CPM)) %>% 
  spread(key = 'sampleid', value = 'cpm') %>% 
  column_to_rownames('pathway') %>% 
  as.matrix
